\documentclass[10pt, a4paper]{article}
\usepackage[top=1.2cm, bottom=1.2cm, left=1cm, right=1cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

% Section headings: normalsize bold + rule — no jarring size jump from \small body
\titleformat{\section}{\normalsize\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{0.6em}{0.5em}

% Kill paragraph spacing globally
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}

% Slight line spread for legibility at small font size
\linespread{1.03}\selectfont

\pagestyle{empty}

\begin{document}

% ── Compact single-line header (saves ~2 lines vs original 3-line header) ──
\begin{center}
{\LARGE \textbf{Karan Mandalam}} \\[2pt]
{\small Bangalore, India $|$ +91-9460596406 $|$ \href{mailto:kmandalam@gmail.com}{kmandalam@gmail.com} $|$ \href{https://linkedin.com/in/mandalam-karan}{linkedin.com/in/mandalam-karan} $|$ \href{https://karan-profile-zeta.vercel.app}{karan-profile-zeta.vercel.app}}
\end{center}

% Reclaim space after header
\vspace*{-1.5em}

\section*{Summary}
\vspace{-0.1em}
%%BEGIN_EDITABLE
{\small Technical Product Manager with 7+ years building API-first, cloud-native integration platforms across CTO and COO offices. Experienced in defining RESTful APIs, webhook-driven lifecycle events, authentication layers, schema governance, and backward-compatible versioning strategies for scalable, secure systems. Shipped event-driven architectures that reduced lead-to-meeting time by 25\%, cut campaign go-live time by 50\%, and drove 5$\times$ organic growth through modular CMS and analytics platforms. Led migration of fragmented legacy workflows into unified integration layers, consolidating ownership, improving observability through structured logging and monitoring, and reducing operational overhead. Comfortable partnering deeply with engineering on feasibility and reliability while aligning platform roadmaps to measurable business outcomes, including AI-enabled automation and production-grade LLM integrations.\par}
%%END_EDITABLE

\section*{Experience}
\vspace{-0.1em}

{\small \textbf{Product Manager, CTO's Office} \hfill 2023 -- 2025 \\
\textit{Miles Education} \hfill Bangalore, India}

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=1.2em, labelsep=0.4em, itemsep=0.2em, topsep=0.4em, parsep=0em]
    \item {\small Owned product strategy and roadmap for platforms across communications, scheduling, CMS, and AI workflows.}
    \item {\small Architected and shipped an event-driven integration platform using API contracts and webhook-based lifecycle events, enabling self-serve business workflows while enforcing authentication, logging, and failure-handling standards.}
    \item {\small Built a consumer-facing scheduling platform on versioned shared APIs with documented schemas, lifecycle events, and backward-compatible contract changes, reducing lead-to-meeting time by $\sim$25\%.}
    \item {\small Launched modular CMS platforms and reusable components with admin playbooks, reducing ops effort by $\sim$40\% and driving $\sim$5x growth in organic traffic.}
    \item {\small Designed and productionized agentic AI workflows, cutting down campaign go-live time by 50\%.}
    \item {\small Led migration of fragmented legacy workflows into a unified, event-driven integration layer, consolidating ownership and improving system observability and reliability.}
\end{itemize}
%%END_EDITABLE

\vspace{0.2em}

{\small \textbf{Program Manager, COO's Office} \hfill 2022 -- 2023 \\
\textit{AlmaBetter} \hfill Bangalore, India}

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=1.2em, labelsep=0.4em, itemsep=0.2em, topsep=0.4em, parsep=0em]
    \item {\small Owned the events and growth platform charter, defining workflows, success metrics, and analytics from scratch.}
    \item {\small Built and optimized event funnels with simplified registration and tracking, doubling enrollments and delivering $\sim$1Cr quarterly impact.}
    \item {\small Designed a Slack-integrated ticketing and workflow system, improving SLA by $\sim$40\% and reducing learning-related tickets by $\sim$25\%.}
    \item {\small Established a technical content production system, increasing average session time by $\sim$30\% and reducing bounce rate by $\sim$40\%.}
\end{itemize}
%%END_EDITABLE

\vspace{0.2em}

{\small \textbf{Product Strategist} \hfill 2020 -- 2022 \\
\textit{upGrad} \hfill Bangalore, India}

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=1.2em, labelsep=0.4em, itemsep=0.2em, topsep=0.4em, parsep=0em]
    \item {\small Owned end-to-end product lifecycle for edtech programs, from discovery and requirements to launch and iteration, maintaining consistent CSAT of 4.5+/5.}
    \item {\small Conducted user interviews and analyzed platform data to introduce interactive learning features, improving customer ratings by $\sim$5\%.}
\end{itemize}
%%END_EDITABLE

\vspace{0.2em}

{\small \textbf{Associate Consultant} \hfill 2018 -- 2020 \\
\textit{Capgemini} \hfill Mumbai, India}

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=1.2em, labelsep=0.4em, itemsep=0.2em, topsep=0.4em, parsep=0em]
    \item {\small Provided L3 production support for Disney's Team Box system, debugging distributed API failures using Splunk and system logs.}
\end{itemize}
%%END_EDITABLE

\section*{Personal Products}
\vspace{-0.1em}

%%BEGIN_EDITABLE
{\small \textbf{MyThirdPlace} --- Built a community and events discovery platform end-to-end, owning product vision, roadmap, and execution across web app, admin tooling, payments, and analytics. Designed an API-first backend with role-based access controls, webhook subscriptions, audit logging, and real-time data flows, enabling secure, scalable operations with production-grade reliability.\par}
%%END_EDITABLE

\vspace{0.2em}

%%BEGIN_EDITABLE
{\small \textbf{MereKapade} --- Built an AI-powered custom apparel platform enabling users to generate, edit, and order personalized designs through guided GenAI workflows. Designed a modular, cloud-native architecture supporting AI generation, visual editing, e-commerce flows, and future fulfillment automation.\par}
%%END_EDITABLE

\section*{Technical Skills}
\vspace{-0.1em}
{\small
\textbf{Product Management:} Product Roadmap Ownership, Platform Product Management, API-as-a-Product \\
\textbf{Platform, Cloud \& Systems:} RESTful API Design, Webhooks, Authentication (OAuth/JWT), API Versioning \& Backward Compatibility, Event-Driven Architectures, Microservices, Cloud-Native Systems (AWS, GCP) \\
\textbf{AI \& Automation:} GenAI Product Integration, RAG Systems, Agentic Workflows, LLM Evaluation \& Observability \\
\textbf{Tools:} Jira, Confluence, Postman, Swagger, GitHub, Splunk, Datadog
}

\section*{Education}
\vspace{-0.1em}
{\small \textbf{BITS Pilani} \hfill 2014 -- 2018 \\
Bachelor of Engineering (B.E.) Hons. \hfill Pilani, India}

\end{document}
