\documentclass[10pt,a4paper]{article}
\usepackage[margin=0.38in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\linespread{1.0}
\titleformat{\section}{\bfseries\small}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{7pt}{3pt}
\setlist[itemize]{leftmargin=*, itemsep=1pt, topsep=2pt, parsep=0pt, partopsep=0pt}
\hyphenation{deviations human-in-the-loop}

\begin{document}
\fontsize{9.5pt}{11pt}\selectfont

\begin{center}
{\LARGE \textbf{Karan Mandalam}} \\[4pt]
Bangalore, India \textbar{} +91-9460596406 \textbar{} \href{mailto:kmandalam@gmail.com}{kmandalam@gmail.com} \\
\href{https://linkedin.com/in/mandalam-karan}{linkedin.com/in/mandalam-karan} \textbar{} \href{https://karan-profile-zeta.vercel.app}{karan-profile-zeta.vercel.app}
\end{center}

\section*{Summary}
%%BEGIN_EDITABLE
AI Product Manager with 7+ years building production systems that combine LLMs, automation, and human-in-the-loop workflows into measurable business outcomes. Hands-on across agentic pipelines, prompt systems, structured outputs, eval loops, and decision-support tools. Delivered systems that improved lead quality by $\sim$20\%, reduced lead-to-meeting time by $\sim$25\%, cut launch cycles by $\sim$50\%, and contributed to 5x organic growth across ₹2Cr+/month acquisition operations. Effective at translating ambiguous AI capabilities into scoped product decisions, rollouts, and post-launch improvement cycles.
%%END_EDITABLE

\section*{Selected Products}

\textbf{Job Search Agent \textbar{} Personal Product}
\begin{itemize}
  \item Built a production multi-agent system with specialized agents for JD parsing, resume tailoring, outreach drafting, fit scoring, and follow-up state — wired with prompt versioning, structured evals, and artifact storage as first-class concerns.
\end{itemize}

\textbf{GTM Automation System \textbar{} Miles Education}
\begin{itemize}
  \item Built production automation across lead capture, lifecycle nudges, event registration, meeting booking, attribution, reporting, and error monitoring; improved lead quality, speed-to-meeting, reporting visibility, and business-user execution speed.
\end{itemize}

\textbf{MyThirdPlace \textbar{} Product}
\begin{itemize}
  \item Built a 0-to-1 community and events product ecosystem with user discovery, participation, referrals and an admin panel with moderation, analytics, and audit controls.
\end{itemize}

\section*{Experience}

\textbf{Independent Consultant \textbar{} AI Product \& GTM Systems \textbar{} 2025 -- Present}
\begin{itemize}
  \item Consulted founders and operators on AI-enabled workflow and GTM systems, translating messy CRM, lifecycle, reporting, and internal-process gaps into scoped workflows, tool decisions, and execution roadmaps.
\end{itemize}

\textbf{Product Manager \textbar{} Tribeca Developers \textbar{} 2025 -- 2025}
%%BEGIN_EDITABLE[Tribeca Developers]
\begin{itemize}
  \item Built a Chief-of-Staff AI bot for CXO teams, turning scattered updates and follow-ups across legal, HR, ops, and reporting into permission-aware decision-support workflows with summaries, human review, audit trails, and PII controls.
\end{itemize}
%%END_EDITABLE

\textbf{Product Manager \textbar{} Miles Education \textbar{} 2023 -- 2025}
%%BEGIN_EDITABLE[Miles Education]
\begin{itemize}
  \item Converted fragmented growth, CRM, and lifecycle operations into structured product workflows across acquisition, activation and retention, improving lead quality by $\sim$20\% and reducing lead-to-meeting time by $\sim$25\%.
  \item Built AI-assisted ops workflows for campaign analysis, content QA, and segmentation review, with human-in-the-loop where brand, accuracy, or revenue risk needed control.
  \item Created attribution and reporting infrastructure for ₹2Cr+/month acquisition spend, standardizing UTM governance, funnel dashboards, and channel-level performance reviews.
  \item Productized marketing execution through self-serve CMS, event, and scheduling systems, cutting launch cycles by $\sim$50\% and contributing to 5x organic traffic growth.
  \item Designed automation guardrails across validation, routing logic, retries, status tracking, and error alerts, reducing manual firefighting across high-volume GTM and lifecycle workflows.
\end{itemize}
%%END_EDITABLE

\textbf{Program Manager \textbar{} AlmaBetter \textbar{} 2022 -- 2023}
%%BEGIN_EDITABLE[AlmaBetter]
\begin{itemize}
  \item Built AlmaBetter's event-led acquisition channel, owning strategy, funnel design, lifecycle operations, and conversion tracking; reduced registration drop-offs to drive $\sim$₹1Cr quarterly revenue impact.
  \item Rebuilt content operations into a predictable production system across planning, ownership, QA, and delivery governance; moved execution $\sim$7 weeks ahead of schedule and reduced content errors by $\sim$90\%.
  \item Rebuilt placement support into a structured program for tracking candidates, reduced interviews-to-placement time by 30\%.
\end{itemize}
%%END_EDITABLE

\textbf{Product Strategist \textbar{} upGrad \textbar{} 2020 -- 2022}
%%BEGIN_EDITABLE[upGrad]
\begin{itemize}
  \item Improved learning-product experience across course structure, assessments, labs, and feedback loops, helping sustain 4.5+ course ratings and increasing engagement across technical programs.
  \item Productized course delivery workflows across planning, vendor coordination, QA, and release tracking, reducing timeline deviations by $\sim$15\% and improving launch predictability.
\end{itemize}
%%END_EDITABLE

\textbf{Associate Consultant \textbar{} Capgemini \textbar{} 2018 -- 2020}
%%BEGIN_EDITABLE[Capgemini]
\begin{itemize}
  \item Automated enterprise CMS migration and support workflows, saving $\sim$2 weeks of manual effort while building hands-on exposure to API logs, incident debugging, releases, and production reliability.
\end{itemize}
%%END_EDITABLE

\section*{Skills and Tools}
\textbf{AI Product \& Systems:} LLM workflows, agentic workflow design, prompt systems, structured outputs, eval loops, human-in-the-loop review, RAG planning, decision-support systems. \\
\textbf{Product \& Execution:} Product discovery, PRDs, roadmap planning, 0-to-1 product building, GTM systems, lifecycle products, stakeholder alignment, rollout planning. \\
\textbf{Automation \& Data:} n8n, API integrations, CRM \& lifecycle automation, workflow orchestration, SQL, GA4, funnel analysis, attribution, dashboarding, Metabase. \\
\textbf{Tools \& Platforms:} HubSpot, Netcore, CleverTap, WebEngage, Supabase, Firebase, PostgreSQL, REST APIs, webhooks, Docker, Vercel, Railway, Google Tag Manager.

\section*{Education}
\textbf{Bachelor of Engineering (B.E.) Hons. \textbar{} BITS Pilani \textbar{} 2014 -- 2018} \\
Pilani, India

\end{document}
