\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\begin{document}

\begin{center}
{\LARGE \textbf{Karan Mandalam}} \\[4pt]
Product Manager \\
Bangalore, India \textbar{} +91-9460596406 \textbar{} \href{mailto:kmandalam@gmail.com}{kmandalam@gmail.com} \\
\href{https://linkedin.com/in/mandalam-karan}{linkedin.com/in/mandalam-karan} \textbar{} \href{https://karan-profile-zeta.vercel.app}{karan-profile-zeta.vercel.app}
\end{center}

\section*{Summary}
%%BEGIN_EDITABLE
Product Manager with 7+ years of experience owning customer-facing and internal products across growth, GTM, and lifecycle surfaces in scaled organizations. Proven track record driving roadmap definition and cross-functional delivery for products supporting $\sim$\$30M ARR, with measurable impact on conversion, efficiency, and user outcomes. Experienced in shipping AI-assisted, multimodal features as part of modern CRM and lifecycle stacks, using data and experimentation to guide decisions.
%%END_EDITABLE

\section*{Experience}

\textbf{Tribeca Developers \textbar{} Turing} \hfill 2025 -- 2025 \\
\textit{Consultant -- Product, Systems \& AI Enablement} \hfill Bangalore, India

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=*, nosep]
  \item Led CXO-facing discovery and delivery of AI-enabled internal products across ops, data access, and executive reporting, translating problem statements into PRDs, vendor evaluations, and shipped solutions.
  \item Built AI system literacy through hands-on work with LLM training and evaluation workflows (RLHF-style feedback, rubric-based evals), contributing across 100+ model tasks and informing human-in-the-loop automation decisions.
\end{itemize}
%%END_EDITABLE

\textbf{Miles Education} \hfill 2023 -- 2025 \\
\textit{Product Manager} \hfill Bangalore, India

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=*, nosep]
  \item Owned product outcomes across acquisition, lifecycle, and internal product surfaces for a $\sim$\$30M ARR business, partnering with engineering, design, marketing, and sales to plan roadmaps and deliver incremental improvements.
  \item Led requirements definition and delivery for multiple customer-facing and internal features across lead management, reporting, and communication flows, improving usability, reliability, and cross-team adoption.
  \item Owned GTM for large-scale programs including events and conclaves, owning registration flows, customer communications, and CRM handoffs; improved lead-to-attendance conversion and reduced manual coordination.
  \item Ran data-informed iteration across WhatsApp, email, and CRM journeys, using funnel and behavioral metrics to improve lifecycle conversion rates by 10--15\% and influence optimization of INR 2Cr+/month in acquisition spend.
  \item Shipped AI-assisted, multimodal CRM and lifecycle features, defining requirements for LLM-driven decisioning and retrieval-backed content; reduced campaign launch cycles and improved CRM execution efficiency.
\end{itemize}
%%END_EDITABLE

\textbf{AlmaBetter} \hfill 2022 -- 2023 \\
\textit{Program Manager -- Product \& Growth} \hfill Bangalore, India

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=*, nosep]
  \item Owned product delivery across learning experience and growth initiatives, working with content, engineering, marketing, and ops teams to ship roadmap items tied to enrollment, completion, and satisfaction metrics.
  \item Led 0-to-1 launch and scale of the Events vertical as a product line, owning registration UX, pricing inputs, communication flows, and analytics; delivered $\sim$INR 1Cr revenue impact in a quarter, with 3x registrations.
  \item Improved learner experience by identifying high-friction support and delivery gaps, shipping a productized ticketing and resolution workflow that reduced turnaround time by $\sim$35\%.
  \item Improved the Placement Assistance Program by streamlining learner and mentor workflows, increasing participation in placement activities by $\sim$30\% and reducing manual coordination for ops teams.
\end{itemize}
%%END_EDITABLE

\textbf{upGrad} \hfill 2020 -- 2022 \\
\textit{Product Strategist} \hfill Bangalore, India

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=*, nosep]
  \item Owned product strategy and roadmap for multiple postgraduate programs, conducting market and learner research to define program vision, curriculum structure, and feature requirements.
  \item Drove learner outcomes through continuous iteration on content, assessments, and delivery workflows using cohort data and feedback, contributing to 4.5+ average course ratings, $\sim$88\% CSAT, and $\sim$70 NPS across cohorts.
\end{itemize}
%%END_EDITABLE

\textbf{Capgemini} \hfill 2018 -- 2020 \\
\textit{Associate Consultant} \hfill Mumbai, India

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=*, nosep]
  \item Contributed to enterprise initiatives, supporting requirements analysis, workflow automation, and production issue resolution in collaboration with engineering and client stakeholders.
\end{itemize}
%%END_EDITABLE

\section*{Projects}

\textbf{MyThirdPlace}

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=*, nosep]
  \item Built and owned a consumer-facing product from concept to launch, defining product vision, roadmap, and core user journeys across discovery, hosting, and participation.
  \item Shipped admin tooling, activity logging, and analytics to support moderation, event operations, and growth tracking.
\end{itemize}
%%END_EDITABLE

\textbf{MereKapade}

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=*, nosep]
  \item Built an AI-assisted custom apparel product, owning end-to-end requirements across intent-to-purchase flows, interactive design, pricing logic, and backend integrations to enable scalable customization.
\end{itemize}
%%END_EDITABLE

\section*{Skills}
\textbf{Product Management:} Roadmap ownership, 0-to-1 and 1-to-n delivery, PRDs \& requirements definition, cross-functional leadership, GTM planning \\
\textbf{AI \& Automation:} AI-assisted CRM features, LLM-driven decisioning, retrieval-backed content, RLHF-style evaluation workflows \\
\textbf{Growth \& Lifecycle:} Funnel optimization, A/B testing, lifecycle campaigns, WhatsApp \& email journeys, multi-touch attribution \\
\textbf{Data \& Analytics:} GA4, Google Tag Manager, Metabase, SQL, Mixpanel, cohort analysis \\
\textbf{Tools:} Jira, Linear, Figma, HubSpot, Netcore, CleverTap, WebEngage, BigQuery

\section*{Education}
\textbf{BITS Pilani} \hfill 2014 -- 2018 \\
B.E. in Computer Science \& Engineering \hfill Rajasthan, India

\end{document}
