\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\begin{document}

\begin{center}
{\LARGE \textbf{Karan Mandalam}} \\[4pt]
Founder's Office \\
Bangalore, India \textbar{} +91-9460596406 \textbar{} \href{mailto:kmandalam@gmail.com}{kmandalam@gmail.com} \\
\href{https://linkedin.com/in/mandalam-karan}{linkedin.com/in/mandalam-karan} \textbar{} \href{https://karan-profile-zeta.vercel.app}{karan-profile-zeta.vercel.app}
\end{center}

\section*{Professional Summary}
%%BEGIN_EDITABLE
Generalist operator with 7+ years working from Founders' offices, owning ambiguous charters across product, growth, and internal systems. Have built and scaled GTM, automation, and reporting platforms supporting INR 2Cr+/month in spend and INR 1Cr+ in incremental revenue impact. Known for turning unclear business goals into executable systems that reduce manual effort, improve decision velocity, and scale without proportional headcount.
%%END_EDITABLE

\section*{Work Experience}

\textbf{Multiple Startups} \hfill 2025 -- 2025 \\
\textit{Consulting -- AI Product \& Systems}

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=*, nosep]
  \item Acted as Founder/Leadership Office operator across orgs, owning ambiguous charters spanning internal platforms, GTM systems, analytics, and decision-support tooling.
  \item Identified and closed high-friction gaps by leading build vs buy evaluations, vendor selection, and tool rollouts.
  \item Designed and shipped internal systems and dashboards for CXO use, consolidating fragmented data into decision-ready views and reducing reliance on manual reporting.
  \item Designed AI-enabled workflows (RAG, agent orchestration, evals, automation) to accelerate experimentation, decision-making, and operational leverage for lean teams.
\end{itemize}
%%END_EDITABLE

\textbf{Miles Education} \hfill 2023 -- 2025 \\
\textit{Product Manager}

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=*, nosep]
  \item Embedded in CEO/CTO office to build scalable growth, CRM, and automation systems.
  \item Built the end-to-end GTM data and attribution backbone (tracking, funnel definitions, reporting), creating a single source of truth that improved lead-quality signal and decision velocity by $\sim$1.2$\times$.
  \item Designed and shipped internal platforms across web, CMS, events, and scheduling, enabling faster experimentation and admin-led iteration, driving $\sim$3$\times$ growth in organic traffic and materially reducing launch turnaround time.
  \item Orchestrated cross-functional workflows across CRM, web, ads, events, and sales, aligning teams on shared states and handoffs and reducing manual coordination and operational friction by $\sim$2$\times$.
  \item Built the MarTech stack with embedded analytics, turning campaigns into repeatable, measurable programs and improving execution reliability by $\sim$3$\times$.
  \item Introduced AI-enhanced workflows across content creation, enrichment, and analysis, shortening experiment-to-insight cycles and increasing execution throughput by $\sim$2$\times$.
\end{itemize}
%%END_EDITABLE

\textbf{AlmaBetter} \hfill 2022 -- 2023 \\
\textit{Founder's Office}

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=*, nosep]
  \item Built and owned the events GTM + ops engine with the COO, integrating growth, content, and automation workflows to drive $\sim$3$\times$ scale in registrations with stronger attendance quality and monetization outcomes.
  \item Re-architected content delivery operations by introducing structured Jira workflows, automation, and QC gates, creating predictable throughput and $\sim$10$\times$ reduction in execution errors across teams.
  \item Set up and scaled a technical content marketing system (blogs, tutorials, creatives) with clear ownership, tracking, and QA, improving discovery, session depth, and SEO-led acquisition performance.
  \item Designed automation-first support and lifecycle systems (onboarding, escalations, drop-off handling), reducing manual load on learning teams and improving reliability across user-facing operations.
\end{itemize}
%%END_EDITABLE

\textbf{upGrad} \hfill 2020 -- 2022 \\
\textit{Product Strategist}

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=*, nosep]
  \item Owned delivery of learning product across content, platform, and learner experience, maintaining 4.5+ CSAT across cohorts.
  \item Built and iterated engagement and retention mechanisms through structured experimentation and workflow discipline, improving learner engagement and completion outcomes by 20\%.
  \item Introduced structured content planning and release workflows across product and academic teams, reducing delivery variance and improving predictability of launches.
\end{itemize}
%%END_EDITABLE

\textbf{Capgemini} \hfill 2018 -- 2020 \\
\textit{Associate Consultant}

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=*, nosep]
  \item Technical consultant tasked with enterprise-scale content migrations and ensuring production stability.
  \item Automated and executed a large-scale CMS migration, reducing delivery time by 15\%.
  \item Provided L3 production support for enterprise systems, diagnosing API and data issues using logs and monitoring tools.
\end{itemize}
%%END_EDITABLE

\section*{Selected Products}

%%BEGIN_EDITABLE
\begin{itemize}[leftmargin=*, nosep]
  \item \textbf{MyThirdPlace:} Built a community and events discovery platform end-to-end, owning product vision, data models, admin tooling, payments, lifecycle workflows, and analytics to support repeatable growth and operational scale.
  \item \textbf{MereKapade:} Built an AI-assisted custom apparel platform guiding users from intent to purchase through interactive, generative design workflows with a modular, extensible product architecture.
\end{itemize}
%%END_EDITABLE

\section*{Skills}
\textbf{Operations \& Strategy:} GTM system design, cross-functional orchestration, build-vs-buy evaluation, vendor selection, reporting \& decision-support systems \\
\textbf{AI \& Automation:} RAG workflows, agent orchestration, GenAI-assisted content \& analysis, automation design (n8n), AI-enabled experimentation \\
\textbf{MarTech \& CRM:} HubSpot, Netcore, CleverTap, WebEngage, attribution modeling, lifecycle \& campaign automation \\
\textbf{Data \& Analytics:} GA4, Google Tag Manager, Metabase, SQL, funnel analysis, cohort tracking \\
\textbf{Tools:} Jira, Confluence, Google Workspace, Notion, Linear

\section*{Education}
\textbf{BITS Pilani} \hfill 2014 -- 2018 \\
Bachelor of Engineering (B.E.) Hons. \hfill Pilani, India

\end{document}
