\documentclass[10pt,a4paper]{article}
\usepackage[margin=0.4in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\linespread{1.02}
\titleformat{\section}{\bfseries\normalsize}{}{0pt}{}
\titlespacing*{\section}{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=*, itemsep=2pt, topsep=2pt, parsep=0pt, partopsep=0pt}

\begin{document}
\fontsize{10pt}{11.5pt}\selectfont

\begin{center}
{\LARGE \textbf{Karan Mandalam}} \\[4pt]
Agentic AI Implementation Consultant \\
Bangalore, India \textbar{} +91-9460596406 \textbar{} \href{mailto:kmandalam@gmail.com}{kmandalam@gmail.com} \\
\href{https://linkedin.com/in/mandalam-karan}{linkedin.com/in/mandalam-karan} \textbar{} \href{https://karan-profile-zeta.vercel.app}{karan-profile-zeta.vercel.app}
\end{center}

\section*{Summary}
%%BEGIN_EDITABLE
Agentic AI and systems implementation specialist with 7+ years delivering production-grade AI-driven workflows and SaaS integrations across go-to-market, customer experience, and operations. Proven at translating ambiguous business problems into scalable agentic systems spanning orchestration, APIs, data pipelines, and observability, and optimizing them through analytics and iteration. Experienced owning the full implementation lifecycle, from discovery and solution architecture to deployment, troubleshooting, and post-go-live performance tuning, while partnering closely with enterprise stakeholders.
%%END_EDITABLE

\section*{Skills \& Tools}
\textbf{Agentic AI:} Agentic AI workflows, autonomous agents, AI copilots, workflow orchestration (n8n), RAG-style systems, NLP automation, NLP $\rightarrow$ SQL agents, prompt design \& evaluation \\
\textbf{SaaS Implementation:} SaaS architecture, CRM \& CX platforms, marketing automation, post-deployment optimization \\
\textbf{Data \& Analytics:} SQL (PostgreSQL), GA4, GTM, funnel analysis, attribution modeling \\
\textbf{Platforms:} HubSpot, Netcore, WebEngage, CleverTap, WhatsApp Business API, Strapi, Supabase, Firebase

\section*{Experience}

\textbf{Product Manager \textbar{} Tribeca Developers \textbar{} 2025 -- 2025}
%%BEGIN_EDITABLE[Tribeca Developers]
\begin{itemize}[leftmargin=*, nosep]
  \item Implemented internal AI enablement workflows and assistive copilots to reduce manual effort in research, reporting, and decision support, improving execution velocity across teams.
  \item Built analytics and reporting frameworks by defining custom fields, data pipelines, and dashboards to give leadership visibility into system performance and operational health.
\end{itemize}
%%END_EDITABLE

\textbf{Product Manager \textbar{} Miles Education \textbar{} 2023 -- 2025}
%%BEGIN_EDITABLE[Miles Education]
\begin{itemize}[leftmargin=*, nosep]
  \item Led end-to-end implementation of agentic, event-driven automation systems using n8n as the orchestration layer, integrating CRM, WhatsApp, email, CMS, and analytics platforms.
  \item Served as solution architect for marketing and CX automation, configuring journeys, triggers, retries, error handling, and monitoring; improved lead quality by $\sim$20\% and reduced lead-to-meeting time by $\sim$25\%.
  \item Built AI-powered workflows including CX chatbots, AI-assisted communication pipelines, and NLP $\rightarrow$ SQL reporting agents to deliver faster insights to business and customer success teams.
  \item Partnered with business, CSM, and ops stakeholders during rollout and post-deployment phases to troubleshoot complex integration issues, refine configurations, and apply best practices, improving system reliability and time-to-value for new workflows.
\end{itemize}
%%END_EDITABLE

\textbf{Growth \& Program Manager -- Learning \& Operations \textbar{} AlmaBetter \textbar{} 2022 -- 2023}
%%BEGIN_EDITABLE[AlmaBetter]
\begin{itemize}[leftmargin=*, nosep]
  \item Re-architected learning operations across content creation, delivery, learner support, and lifecycle communications by introducing structured workflows and automation, reducing operational errors by $\sim$90\%.
  \item Embedded GenAI-assisted content development workflows into the production process, improving turnaround time and delivery consistency while reducing manual review overhead.
  \item Designed and deployed event and lifecycle systems with experimentation-led funnel optimization, driving $\sim$2$\times$ increase in registrations and 20--25\% improvement in learner conversion and retention.
\end{itemize}
%%END_EDITABLE

\textbf{Product Strategist \textbar{} upGrad \textbar{} 2020 -- 2022}
%%BEGIN_EDITABLE[upGrad]
\begin{itemize}[leftmargin=*, nosep]
  \item Owned end-to-end delivery of learning products with cross-functional teams; maintained 4.5+ CSAT across cohorts.
  \item Improved delivery workflows and vendor operations, reducing timeline deviation by $\sim$15\% without quality loss.
\end{itemize}
%%END_EDITABLE

\textbf{Associate Consultant \textbar{} Capgemini \textbar{} 2018 -- 2020}
%%BEGIN_EDITABLE[Capgemini]
\begin{itemize}[leftmargin=*, nosep]
  \item Automated CMS migration workflows, reducing delivery time by $\sim$2 weeks on enterprise delivery cycles.
  \item L3 production support for mission-critical reservation system: debugged API issues via logs/observability (Splunk, AWS), drove incident resolution with global stakeholders.
\end{itemize}
%%END_EDITABLE

\section*{Products}

\textbf{MyThirdPlace \textbar{} Community \& events discovery platform}
%%BEGIN_EDITABLE[MyThirdPlace]
\begin{itemize}[leftmargin=*, nosep]
  \item Designed and built the product end-to-end, owning problem definition, roadmap, and system architecture across user experience, admin tooling, payments, and analytics.
  \item Implemented modular workflows and automation to support repeatable growth, event operations, and privacy-aware participant handling without manual ops overhead.
\end{itemize}
%%END_EDITABLE

\textbf{MereKapade \textbar{} AI-powered custom apparel platform}
%%BEGIN_EDITABLE[MereKapade]
\begin{itemize}[leftmargin=*, nosep]
  \item Built an AI-assisted product that guides users from intent to purchase through interactive, generative design workflows, reducing friction in custom apparel creation.
  \item Designed a modular, API-first architecture to support AI-driven customization, experimentation, and future model upgrades without platform rewrites.
\end{itemize}
%%END_EDITABLE

\section*{Education \& Certifications}
\textbf{B.E. Computer Science \& Engineering \textbar{} BITS Pilani}

\end{document}
